Kalman tracking and parameter estimation of continuous gravitational waves with a pulsar timing array: inclusion of pulsar terms

### 2023-11-21 manuscript/manuscript_2/paper.tex
some clean up to resemble canonical

We apply the Kalman filter in conjunction with nested sampling in order to infer the

@@

\begin{figure*}
	\includegraphics[width=\textwidth, height =\textwidth ]{images/stacked_GW_plot_small_h_definitive2}
	\caption{Posterior distribution of the GW source parameters $\boldsymbol{\theta}_{\rm gw}$ for the representative system in Table \ref{tab:parameters_and_priors}, for nine realisations of the noise processes, with curves coloured uniquely. The horizontal and vertical orange lines indicate the true injected values. The contours in the two-dimensional histograms mark the (0.5, 1, 1.5, 2)-$\sigma$ levels after marginalizing over all but two parameters. The one-dimensional histograms correspond to the joint posterior distribution marginalized over all but one parameter. The supertitles of the one-dimensional histograms record the posterior median and the 0.16 and 0.84 quantiles of the median realisation. We plot the scaled variables $10^9 \Omega$ (units: ${\rm rad \, s^{-1}}$) and $10^{15} h_0$. The Kalman filter and nested sampler estimate accurately all seven parameters in ${\boldsymbol{\theta}}_{\rm gw}$. The horizontal axes span a subset of the prior domain for all seven parameters. The known, injected value lies within the 90\% credible interval for \textcolor{red}{X} out of the 63 combinations of seven parameters and nine noise realizations. There is an appreciable dispersion among the peaks of the one-dimensional posteriors, with coefficient of variation \textcolor{red}{X} across the 63 combinations.}
	\label{fig:corner_plot_1}
\end{figure*}

	\begin{figure}
	\includegraphics[width=\columnwidth, height =\columnwidth ]{images/corner_lowSNR_chi}
	\caption{hellow}
	\label{fig:corner_plot_3}
\end{figure}

>>>>

We apply the Kalman filter in conjunction with nested sampling in order to infer $p({\boldsymbol{\theta}} | {\boldsymbol{Y}})$ .  \newline

@@

% stacked_GW_plot_small_h_definitive2
\begin{figure*}
	\includegraphics[width=\textwidth, height =\textwidth ]{example-image-a}
	\caption{Posterior distribution of the GW source parameters $\boldsymbol{\theta}_{\rm gw}$ for the representative system in Table \ref{tab:parameters_and_priors}, for nine realisations of the noise processes, with curves coloured uniquely. The horizontal and vertical orange lines indicate the true injected values. The contours in the two-dimensional histograms mark the (0.5, 1, 1.5, 2)-$\sigma$ levels after marginalizing over all but two parameters. The one-dimensional histograms correspond to the joint posterior distribution marginalized over all but one parameter. The supertitles of the one-dimensional histograms record the posterior median and the 0.16 and 0.84 quantiles of the median realisation. We plot the scaled variables $10^9 \Omega$ (units: ${\rm rad \, s^{-1}}$) and $10^{15} h_0$. The Kalman filter and nested sampler estimate accurately all seven parameters in ${\boldsymbol{\theta}}_{\rm gw}$. The horizontal axes span a subset of the prior domain for all seven parameters. The known, injected value lies within the 90\% credible interval for \textcolor{red}{X} out of the 63 combinations of seven parameters and nine noise realizations. There is an appreciable dispersion among the peaks of the one-dimensional posteriors, with coefficient of variation \textcolor{red}{X} across the 63 combinations.}
	\label{fig:corner_plot_1}
\end{figure*}

%images/corner_lowSNR_chi
	\begin{figure}
	\includegraphics[width=\columnwidth, height =\columnwidth ]{example-image-b}
	\caption{hellow}
	\label{fig:corner_plot_3}
\end{figure}
